Proof No Diamond (3 layers)

### 2024-01-15 Paper/introduction.tex

In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers. This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots

In this context, application of DNNs in safety critical applications is therefore cautiously envisioned. For that to happen at a large scale, hard guarantees should be provided, so that to avoid tremendous consequences. It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade offs from exact computation but slow (e.g. Marabou/Reluplex), up to very efficient but also incomplete (e.g. ERAN-DeepPoly). To benchmark these tools, a competition has been run since 2019, namely VNNcomp. The current overall better performing tool is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs down to very efficient on larger DNNs.

>>>>

In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers. This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations 
\cite{szegedy}\dots

In this context, application of DNNs in safety critical applications is cautiously envisioned. For that to happen at a large scale, hard guarantees should be provided, so that to avoid dramatic consequences. It is the reason for the developpement of (hard) verification tools since 2016, with now many tools with different trade-offs from exact computation but slow (e.g. Marabou \cite{katz2019marabou}/Reluplex\cite{Reluplex}), up to very efficient but also incomplete (e.g. ERAN-DeepPoly \cite{deeppoly}). To benchmark these tools, a competition has been run since 2019, namely VNNcomp. The current overall better performing verifier is $\alpha$-$\beta$-Crown, a fairly sophisticately engineered tool based mainly on "branch and bound", and which can scale all the way from complete on smaller DNNs up to very efficient on larger DNNs.
